### 2022-01-26 input/proposal.tex
preamble section 3

To provide lazy and dynamic logical partitioning in dynamic networks
using scoped broadcast, all live \processes must collaborate to
disseminate messages that notify new or removed sources to all and
only interested \processes. This section reviews step-by-step the
properties that allow \processes to converge to the desired state
together. It first defines scoped broadcast, then uses it to guarantee
consistent partitioning when a \process can only become a new source
in the system. It highlights the issue when a \process can also remove
its status of source. It shows that using local knowledge and scoped
broadcast, \processes can still reach dynamic consistent partitioning
when they are able to detect possible blocking conditions in the
dissemination of required notifications.

>>>>

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications.  This also applies to dynamic networks where nodes
join, leave, or crash at any time.
